\thetitle

### 2021-05-20 writing/paper.tex
fix small words, vspace for table on pg. 4
move overfullrule to top of paper file so it's easy to turn off
turn of Acknws so we don't forget

\documentclass[acmsmall]{acmart}
% \settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Programming language theoreticians develop blame assignment systems and
  prove blame theorems for gradually typed programming languages.
  Practical implementations of gradual typing almost completely ignore the
  idea of blame assignment.  This contrast raises the question whether
  blame provides any value to the working programmer and poses
  the challenge of how to evaluate the effectiveness of blame assignment
  strategies. This paper contributes (1) the first evaluation method for
  blame assignment strategies and (2) the results from applying it to
  three different semantics for gradual typing. These results cast doubt to
  the theoretical effectiveness of blame. In most scenarios,  strategies
  with imprecise blame assignment are as helpful to a rationally acting
  programmer as strategies with provably correct blame.
\end{abstract}

@@

%% Acknowledgments
%%\begin{acks}                 
  %% acks environment is optional
  %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
%%\end{acks}

>>>>

\documentclass[acmsmall]{acmart}
\overfullrule=.1mm

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Programming language theoreticians develop blame assignment systems and
  prove blame theorems for gradually typed programming languages.
  Practical implementations of gradual typing almost completely ignore the
  idea of blame assignment.  This contrast raises the question whether
  blame provides any value to the working programmer and poses
  the challenge of how to evaluate the effectiveness of blame assignment
  strategies. This paper contributes (1) the first evaluation method for
  blame assignment strategies and (2) the results from applying it to
  three different semantics for gradual typing. These results cast doubt on
  the theoretical effectiveness of blame in gradual typing. In most scenarios, strategies
  with imprecise blame assignment are as helpful to a rationally acting
  programmer as strategies with provably correct blame.
\end{abstract}

@@

%% Acknowledgments
\begin{acks}                 
Felleisen and Greenman were partly supported by NSF grants SHF
1763922. Greenman also received support from a CRA-NSF Post-doctoral
fellowship grant. Dimoulas and Felleisen wish to thank Max New for
extensive discussions of the early ides in this paper. 
\end{acks}
